Estimating associations between childhood exposure to non-persistent endocrine disruptors, corticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2023-12-19 output/paper/manuscript.qmd
Added list tables and figures for main results.
Merged tables and figures for marginal effects into forest plots.
Writing description results. Trying to merge forest plots by outcome.

- Use an uppercase italic letter "P", and the values should not be bolded. Indicate whether are 1- or 2-sided.
- Include the number of observations for each analysis after accounting for missing data. Include numeric data within figures (e.g., forest plots), or provide tables with corresponding numeric data for all figures.

@@

{{< include _tables.qmd >}}

@@

{{< include _si.qmd >}}

>>>>

The effective sample sizes before and after balancing weights estimation are presented in Tables [-@supptbl-balance-1; -@supptbl-balance-2; -@supptbl-balance-3], while basic summary statistics of the estimated balancing weights are presented in Tables [-@supptbl-weights-1; -@supptbl-weights-2; -@supptbl-weights-3]. As expected, the median value of the weights for each exposure was close to $1.00$.

@Fig-marginal-1 presents the forest plot for the marginal effects of the non-persistent \acr{edcs} on \acr{hitrtse}. Overall, a cohort-specific increase in the levels of the exposures from the 10th to the 90th percentiles was associated with a positive marginal contrast, indicating an increase in the values of \acr{hitrtse}. Most of the \acr{ci} included the null effect, though. Statistically significant associations were observed for the phenol MEPA (\acr{mc} = $0.042$, $95\%$ \acr{ci}: $0.013, 0.071$), and the phthalate metabolites oxo-MiNP (\acr{mc} = $0.023$, $95\%$ \acr{ci}: $0.003, 0.044$), oh-MiNP (\acr{mc} = $0.039$, $95\%$ \acr{ci}: $0.001, 0.076$), and MEHP (\acr{mc} = $0.036$, $95\%$ \acr{ci}: $0.008, 0.063$). The \acr{opp} DETP was strongly negatively associated with \acr{hitrtse} (\acr{mc} = $-0.026$, $95\%$ \acr{ci}: $-0.054, 0.001$).

Figures [-@fig-marginal-2-cortisolprod; -@fig-marginal-2-cortisoneprod; -@fig-marginal-2-corticosteroneprod; -@fig-marginal-2-11b] present the forest plots for the marginal effects of the non-persistent \acr{edcs} on cortisol production, cortisone production, corticosterone production, and 11bHSD activity, respectively.

@Fig-marginal-3 presents the forest plot for the marginal effects of the corticosteroids on \acr{hitrtse}.

Results are presented as effect estimate of the marginal contrast and the $95\%$ \acr{ci}.

suppfig-adrfs-rq...

@@

<!-- {{< include _tables.qmd >}} -->

@@

<!-- {{< include _si.qmd >}} -->
